MIP-GNN: A data-driven tool for guiding combinatorial solvers

### 2020-08-19 paper/main.tex
Cont. implementing new model.

\paragraph{Related work} Discuss related work.
\begin{itemize}
	\item GNNs to solve MIPs/comb. optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gasse+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},

@@

\cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree

>>>>

\paragraph{Related work} Discuss related work.
\begin{itemize}
	\item GNNs to solve MIPs/comb. optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gas+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},

@@

\cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds
